### 2017-11-29 submission/manuscript.Rmd
add missing result and correct a grammar error

The genus based models showed an AUC decrease in model classification on the training set for both stool and tissue studies [Figure S2-S3]. With respect to the test sets, comprised of genera data from other studies, both the all genera model and CRC-associated models had a similar ability to detect adenomas or carcinomas [Figure S4-S6]. The AUC for classification of adenomas was lower than carcionmas for both tissue and stool [Figure S4-S6].

The OTU based models for both fecal and tissue (matched and unmatched) samples, showed an AUC decrease when only OTUs from the CRC-associated genera are used versus full community of OTUs [Figure 4 & 5]. This decrease is observed in both adenoma and carcinoma groups [Figure 4 & 5] with the largest difference in median AUC for stool being in carcinoma classification [Figure 4B] and for tissue being in adenoma [Figure 5A].

>>>>

The genus based models showed an AUC decrease in model classification on the training set for both stool and tissue studies [Figure S2-S3]. With respect to the test sets, comprised of genera data from other studies, both the all genera model and CRC-associated models had a similar ability to detect adenomas or carcinomas [Figure S4-S6]. The AUC for classification of adenomas was lower than carcionmas for both tissue and stool [Figure S4-S6]. Interestingly, the AUC for the classification of carcinoma was consistently lower for the tissue models than the stool models [Figure S4-S6].

The OTU based models for both fecal and tissue (matched and unmatched) samples, showed an AUC decrease when only OTUs from the CRC-associated genera are used versus the full community of OTUs [Figure 4 & 5]. This decrease is observed in both adenoma and carcinoma groups [Figure 4 & 5] with the largest difference in median AUC for stool being in carcinoma classification [Figure 4B] and for tissue being an adenoma [Figure 5A].

### 2017-11-29 submission/manuscript.tex
add missing result and correct a grammar error

The genus based models showed an AUC decrease in model classification on
the training set for both stool and tissue studies {[}Figure S2-S3{]}.
With respect to the test sets, comprised of genera data from other
studies, both the all genera model and CRC-associated models had a
similar ability to detect adenomas or carcinomas {[}Figure S4-S6{]}. The
AUC for classification of adenomas was lower than carcionmas for both
tissue and stool {[}Figure S4-S6{]}.

The OTU based models for both fecal and tissue (matched and unmatched)
samples, showed an AUC decrease when only OTUs from the CRC-associated
genera are used versus full community of OTUs {[}Figure 4 \& 5{]}. This
decrease is observed in both adenoma and carcinoma groups {[}Figure 4 \&
5{]} with the largest difference in median AUC for stool being in
carcinoma classification {[}Figure 4B{]} and for tissue being in adenoma
{[}Figure 5A{]}.

>>>>

The genus based models showed an AUC decrease in model classification on
the training set for both stool and tissue studies {[}Figure S2-S3{]}.
With respect to the test sets, comprised of genera data from other
studies, both the all genera model and CRC-associated models had a
similar ability to detect adenomas or carcinomas {[}Figure S4-S6{]}. The
AUC for classification of adenomas was lower than carcionmas for both
tissue and stool {[}Figure S4-S6{]}. Interestingly, the AUC for the
classification of carcinoma was consistently lower for the tissue models
than the stool models {[}Figure S4-S6{]}.

The OTU based models for both fecal and tissue (matched and unmatched)
samples, showed an AUC decrease when only OTUs from the CRC-associated
genera are used versus the full community of OTUs {[}Figure 4 \& 5{]}.
This decrease is observed in both adenoma and carcinoma groups {[}Figure
4 \& 5{]} with the largest difference in median AUC for stool being in
carcinoma classification {[}Figure 4B{]} and for tissue being an adenoma
{[}Figure 5A{]}.
